\textbf{Response Letter}

### 2018-12-02 doc/aij18/major-revision/letter.tex
Updated LOUGA response

\textcolor{blue}{As per the reviewer's recommendation, we requested the code of LOUGA to the first author of the publication entitled \emph{LOUGA: learning planning operators using genetic algorithms}, which was published in the Pacific Rim Knowledge Acquisition Workshop. The author of LOUGA promptly provided us with the code, so we would first like to thank him for his gentle response. However, the issue we faced with LOUGA is that we were not able to automate the processing and output of the results. LOUGA throws results in a graphical interface, which makes it hard to easily retrieve the data to be subsequently processed. Since the input of our automated process for extracting the experimental results are plain text files, we could not adapt the graphical output of LOUGA to our required input. Nevertheless, we did test a couple of .... FALTA POR COMPLETAR}

>>>>

\textcolor{blue}{As per the reviewer's recommendation, we requested the code of LOUGA to the first author of the publication entitled \emph{LOUGA: learning planning operators using genetic algorithms}, which was published in the Pacific Rim Knowledge Acquisition Workshop. The author of LOUGA promptly provided us with the code, so we would first like to thank him for his gentle response. However, the issue we faced with LOUGA is that this system is built as a graphical interface application, which makes it impossible to automate the model learning process and evaluation process via a script for the 154 cases tested. Nevertheless, we did manually test a few cases for the \emph{blocksworld}, \emph{floor-tile}, \emph{n-puzzle} and \emph{transport} domains. The results showed similar performance among the two approaches, with each one performing better in two of the four domains tested.}
